\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-10-04 papers/methods/paper.tex
Initial rick comments

\subsubsection{Correcting biased summary statistics}

With the {\green reported summary statistics $\hat{\eta}$ being biased} and their uncertainty under-reported, we face a significant challenge in supernova cosmology. We must either correct the observables to remove the biases introduced by the intrinsic dispersion of the underlying population, or incorporate this dispersion into our model. We must also do this without assuming a specific dispersion model -- either the {\gten} or {\celeven} model.

We model the extra dispersion only in colour, and do so by adding extra independent uncertainty on the colour observation. We note that extra dispersion in magnitude (from coherent scatter) is absorbed completely by the width of the underlying magnitude population (discussed in Section \ref{sec:underlying}) without introducing cosmological bias, which is not true of the colour term, hence the requirement for modelling additional colour dispersion. Tests on incorporating extra dispersion on stretch as well show that stretch is less biased than colour, and cause negligible bias in cosmology.

As shown in \citep{Kessler2013}, the extra colour dispersion shows heavy redshift dependence, increasing with redshift. As the extra dispersion may arise from underlying supernova physics, rather than Malmquist bias, we decide to incorporate redshift dependence in our extra uncertainty. We thus add $\kappa_0 + \kappa_1 z$ to our observed colour uncertainty (in quadrature). The $\kappa$ parameters are highly degenerate with the width of the intrinsic colour population $\sigma_c$. We subject them to Cauchy priors centered on zero and with width $0.05$, where $\kappa$ is bounded between $0$ and $0.05$. We pick this maximum value to allow extra dispersion without completely subsuming the intrinsic population widths due to the severe degeneracy, where this maximum value easily encapsulates the determined dispersion according to the results of \citet{Kessler2013}. As such, our combined covariance on the observation $\hat{\eta}$ is given by $\mathcal{C}_{\rm tot} = \mathcal{C} + {\rm DiagMatrix}\left[0, 0, (\kappa_0 + \kappa_1 z)^2\right]$.

@@

@@

In order to verify our model we run it through stringent tests. First, we validate on toy models, verifying that we recover accurate cosmology in highly constraining datasets. We then validate our model on SNANA simulations based on a collection of low redshift surveys and the DES three-year spectroscopic sample.

@@

\begin{enumerate}[1.]
	\item Draw a redshift from a power law distribution. For the low redshift survey this is $\mathcal{U}(0.0004, 0.01)^{0.5}$, and for the DES-like survey this is $\mathcal{U}(0.008, 1.0)^{0.3}$.
	\item Draw a true absolute magnitude, stretch and colour from the respective distributions $\mathcal{N}(-19.3, 0.1)$, $\mathcal{N}(0, 1)$, $\mathcal{N}(0, 0.1)$.
	\item Draw a random mass probability from $\mathcal{U}(0, 1)$ and calculate the mass-brightness correction using $\delta(0) = 0.08$, $\delta(0)/\delta(\infty) = 0.5$, and equation \eqref{eq:mass}.
	\item Calculate $\mu(z)$ given the drawn redshift and cosmological parameters $\Omega_m = 0.3$, $w = -1$. Use this to determine the true apparent magnitude of the object $m_B$ using equation \eqref{eq:l2}.
	\item Determine if the SNIa is detected using detection probability $P(S|m_B) = \mathcal{N}^{\rm skew}(13.72, 1.35, 5.87)$ for the low redshift survey (numeric values obtained by fitting to existing low redshift data). For the DES-like survey, accept with probability $P(S|m_B) = \Phi^C(23.14, 0.5)$. Repeat from step one until we have a supernova that passes.
	\item Add independent, Gaussian observational error onto the true $m_B$, $x_1$, $c$ using Gaussian widths of $0.04$, $0.2$, $0.03$ respectively (following the mean uncertainty for DES-like SNANA simulations). Add extra colour uncertainty in quadrature of $\kappa_0 + \kappa_1 z$, where $\kappa_0 = \kappa_1 = 0.03$.
\end{enumerate}

For supernova-independent uncertainty, the selection functions (a skew normal for low-redshift and an error function for high-redshift) are given independent uncertainty of $0.01$ on all parameters (mean and width for the CDF selection function, and mean, width and skewness for the skew normal selection function). Draw from each survey simulation until we have 1000 LowZ supernovae and 1000 DES-like supernovae, representing a statistical sample of greater power than the estimated 350 supernovae for the combined DES three-year and low-redshift spectroscopic analysis. Sample data for 1000 high and low redshift supernovae are shown in Figure \ref{fig:simple_pop}, confirming the presence of strong selection effects in both toy surveys, as designed.

@@

@@

Simulations (using the SNANA package) follow the observational schedule and observing conditions for the DES and LowZ surveys, where the LowZ sample is comprised of CfA3 \citep{Hicken2009, Hicken2009a}, CfA4 \citep{Hicken2012} and CSP \citep{Contreras2010,Folatelli2010,Stritzinger2011}.

In addition to the improvements in the scatter models over the simple data, we also include peculiar velocities for the LowZ sample, and our full treatment of systematics. Our simulated populations are sourced from \citet[][hereafter {\sk}]{Scolnic2016} and shown in Table \ref{tab:dist}. Initial tests were also done with a second, Gaussian population with colour and stretch populations centered on zero and with respective width $0.1$ and $1$, however cosmological parameters were not impacted by choice of the underlying population and we continue using only the {\sk} population for computational efficiency. The selection effects were quantified by comparing all the generated supernovae to those that pass our simulated cuts, as shown in Figure~\ref{fig:sf_snana}. It is from this simulation that our analytic determination of the selection functions for the LowZ and DES survey are based. We run two simulations to determine the efficiency using the {\gten} and {\celeven} scatter models and find no difference in the Malmquist bias between the two models.

@@

\begin{table*}
	\centering
	\caption{Standardisation parameters and base intrinsic scatter parameter results for the 100 fits to {\gten} and {\celeven} simulations. We show the average parameter mean and standard deviation, with the simulation scatter shown in brackets. Truth values for the simulations are $\alpha=0.15$, $\langle M_B \rangle = -19.365$, $\beta_{\rm G10} = 3.1$, $\beta_{\rm C11} = 3.8$.  The width of the intrinsic scatter does not have an input truth value as it is determined from the scatter model, with {\gten} having 70\% achromatic scatter and {\celeven} only having 25\% achromatic scatter.}
	\label{tab:standardisation}
	\begin{tabular}{l|ccccc}
		\hline
		Model & $\alpha$ & $\beta$ & $\langle M_B \rangle$ & $\sigma_{m_B}^0$ &  $\sigma_{m_B}^1$ \\
		\hline
		{\gten} Stat + Syst  & $0.152\pm0.009\ (0.008)$ & $ 3.44\pm0.19\ (0.18)$ & $-19.367\pm0.028\ (0.015)$ & $0.070\pm0.022\ (0.018)$ & $0.073\pm0.025\ (0.022)$\\
		{\gten}  Stat         & $0.150\pm0.008\ (0.008)$ & $3.43\pm0.20\ (0.17)$ & $-19.374\pm0.016\ (0.013)$ & $0.069\pm0.023\ (0.019)$ & $0.072\pm0.026\ (0.023)$\\
		{\celeven} Stat + Syst  &  $0.152\pm0.009\ (0.007)$ & $3.76\pm0.15\ (0.13)$ & $-19.351\pm0.030\ (0.018)$ & $0.024\pm0.016\ (0.011)$ & $0.029\pm0.020\ (0.014)$ \\
		{\celeven} Stat         &  $0.150\pm0.008\ (0.007)$ & $3.75\pm0.16\ (0.13)$ & $-19.359\pm0.016\ (0.015)$ & $0.025\pm0.016\ (0.012)$ & $0.027\pm0.020\ (0.015)$\\
		\hline
	\end{tabular}
\end{table*}

@@

\begin{table}
	\centering
	\caption{Parameter Correlations with $w$ for the combined 100 simulation fits. Correlations for the LowZ band systematics and the latent parameters representing selection function uncertainty are not shown but have negligible correlation.}
	\label{tab:parameter_correlations}
	\begin{tabular}{c|cc}
		Parameter & {\gten} Stat+Syst & {\celeven} Stat+Syst  \\
		\hline
		$\Omega_m$ &   -0.19 &     -0.21     \\
		$\alpha$ &   -0.17 &     -0.20     \\
		$\beta$ &   -0.29 &     -0.23     \\
		$\langle M_B \rangle$ &    0.68 &      0.66     \\
		$\sigma_{\rm m_B}^{0}$ &    0.04 &      0.07     \\
		$\sigma_{\rm m_B}^{1}$ &    0.23 &      0.18     \\
		$\sigma_{x_1}^{0}$ &    0.04 &      0.03     \\
		$\sigma_{x_1}^{1}$ &    0.05 &      0.01     \\
		$\sigma_{c}^{0}$ &    0.01 &      0.11     \\
		$\sigma_{c}^{1}$ &    0.08 &      0.04     \\
		$\alpha_c^{0}$ &   -0.04 &      0.04     \\
		$\alpha_c^{1}$ &    0.03 &      0.01     \\
		$\kappa_{c0}^{0}$ &   -0.10 &     -0.05     \\
		$\kappa_{c0}^{1}$ &   -0.20 &     -0.17     \\
		$\kappa_{c1}^{0}$ &   -0.05 &     -0.01     \\
		$\kappa_{c1}^{1}$ &   -0.01 &      0.01     \\
		%$s_c^{0}$ &    0.00 &      0.01     \\
		$\delta(0)$ &    0.00 &      0.00     \\
		$\delta(\infty)/\delta(0)$ &    0.00 &      0.00     \\
		$\langle x_1^{0} \rangle$ &   -0.01 &     -0.05     \\
		$\langle x_1^{1} \rangle$ &   -0.02 &      0.02     \\
		$\langle x_1^{2} \rangle$ &   -0.04 &     -0.04     \\
		$\langle x_1^{3} \rangle$ &   -0.03 &     -0.06     \\
		$\langle x_1^{4} \rangle$ &   -0.06 &     -0.06     \\
		$\langle x_1^{5} \rangle$ &    0.04 &      0.02     \\
		$\langle x_1^{6} \rangle$ &    0.04 &      0.04     \\
		$\langle x_1^{7} \rangle$ &    0.08 &      0.03     \\
		$\langle c^{0} \rangle$ &   -0.05 &     -0.12     \\
		$\langle c^{1} \rangle$ &    0.11 &      0.03     \\
		$\langle c^{2} \rangle$ &    0.11 &      0.06     \\
		$\langle c^{3} \rangle$ &    0.14 &      0.04     \\
		$\langle c^{4} \rangle$ &   -0.11 &     -0.11     \\
		$\langle c^{5} \rangle$ &   -0.15 &     -0.08     \\
		$\langle c^{6} \rangle$ &   -0.12 &     -0.13     \\
		$\langle c^{7} \rangle$ &   -0.12 &     -0.06     \\
		$\delta [ {\rm SALT}_0 ]$ &    0.05 &      0.05     \\
		$\delta [ {\rm SALT}_1 ]$ &   -0.01 &      0.02     \\
		$\delta [ {\rm SALT}_2 ]$ &   -0.10 &     -0.09     \\
		$\delta [ {\rm SALT}_3 ]$ &   -0.03 &     -0.03     \\
		$\delta [ {\rm SALT}_4 ]$ &    0.08 &      0.09     \\
		$\delta [ {\rm SALT}_5 ]$ &    0.01 &      0.02     \\
		$\delta [ {\rm SALT}_6 ]$ &    0.05 &      0.07     \\
		$\delta [ {\rm SALT}_7 ]$ &   -0.11 &     -0.10     \\
		$\delta [ {\rm SALT}_8 ]$ &    0.01 &      0.02     \\
		$\delta [ {\rm SALT}_9 ]$ &    0.02 &      0.02     \\
		$\delta [ {\rm MWE}_{B-V} ]$ &    0.03 &      0.02     \\
		$\delta [ {\rm HST Calib} ]$ &   -0.07 &     -0.07     \\
		$\delta [ v_{\rm pec} ]$ &    0.00 &     -0.01     \\
		$\delta [ {\rm \delta z } ]$ &    0.01 &      0.00     \\
		$\delta [ \Delta g ]$ &    0.05 &      0.11     \\
		$\delta [ \Delta r ]$ &    0.16 &      0.10     \\
		$\delta [ \Delta i ]$ &   -0.16 &     -0.18     \\
		$\delta [ \Delta z ]$ &   -0.26 &     -0.26     \\
		$\delta [ \Delta \lambda_g ]$ &    0.16 &      0.20     \\
		$\delta [ \Delta \lambda_r ]$ &    0.05 &      0.06     \\
		$\delta [ \Delta \lambda_i ]$ &    0.00 &     -0.01     \\
		$\delta [ \Delta \lambda_z ]$ &    0.09 &      0.07     \\
		\hline
	\end{tabular}
\end{table}

@@

Points of maximum posterior for 100 data realisations are shown in Figure \ref{fig:bulk_posterior}. The parameter bounds and biases for $w$ are listed in Table \ref{tab:bulk_summary},  and secondary parameters are shown in Table \ref{tab:standardisation}. Our recovered results for $w$ are all within $0.5\sigma$ of the true values of $w=-1$. Table \ref{tab:standardisation} shows a clear difference in both $\beta$ and $\sigma_{m_B}$ across the {\gten} and {\celeven} simulations. As expected, the {\celeven} simulations recover a far smaller intrinsic magnitude scatter, giving results of approximately $0.025$ when compared to the result of $0.070$ for the {\gten} simulations. The extra smearing of the {\celeven} model does not result in a biased $\beta$ value, with recovery of $\beta\approx3.76$ close to the input truth value of $3.8$, however the $\beta$ recovery for the {\gten} simulations is biased high, finding $\beta\approx3.44$ with an input of $3.1$. Interestingly, $w$-bias is only found for the {\celeven} simulations.

@@

We compare the results of our model against those of the BBC method \citep{Kessler2017}. BBC has been used in prior analyses, such as the Pantheon sample analysis of \citet{Scolnic2017}. As a leading supernova cosmology method, it provides a good consistency as to the current levels of accuracy in recovering cosmological parameters.

To this end, we take the results of the BBC method also run on our set of 200 validation simulations and compare the recovered $w$ values to those of our method. The results are detailed in Table \ref{tab:bulk_summary_bbc}, and a scatter plot of the simulation results is presented in Figure \ref{fig:bulk_comparison}.

@@

\begin{table}
	\centering
	\caption{Characterising the bias on $w$ using the 100 simulations for the {\gten} scatter model and 100 simulations for {\celeven} scatter model. The mean $w$ value for our method and BBC are presented, along with the mean when averaging the difference between our method and BBC for each individual simulation. Finally, we also characterise the scatter between the methods in the final row. Averages are computed giving each simulation sample the same weight. In the model, $\Delta$ represents Steve - BBC. The final row shows the scatter between Steve and BBC for the different simulations.}
	\label{tab:bulk_summary_bbc}
	\begin{tabular}{l|ccc}
		\hline
		Model & {\gten} & {\celeven} & ({\gten} + {\celeven}) \\
		\hline
		Steve $\langle w \rangle$           & $-0.998\pm0.007$ & $-0.945\pm0.007$ & $-0.972\pm0.006$\\
		BBC $\langle w \rangle$             & $-1.044\pm0.006$ & $-0.978\pm0.007$ & $-1.010\pm0.005$ \\
		$\Delta$  $\langle w \rangle$  & $+0.044\pm0.006$ & $+0.033\pm0.006$ & $+0.038\pm0.004$ \\
		\hline
		$\Delta$  $\sigma_w$           & $0.057\pm0.004$ & $0.062\pm0.004$ & $0.060\pm0.003$ \\
		\hline
	\end{tabular}
\end{table}

>>>>

@@

\subsection{Correcting biased summary statistics}

With the {\green reported summary statistics $\hat{\eta}$ being biased and their uncertainty under-reported, we face a significant challenge utilising these statistics naively in supernova cosmology}. We must either correct the observables to remove the biases introduced by the intrinsic dispersion of the underlying population, or incorporate this dispersion into our model. We must also do this without assuming a specific dispersion model -- either the {\gten} or {\celeven} model.

We model the extra dispersion only in colour, and do so by adding extra independent uncertainty on the colour observation {\green $\hat{c}$}. We note that extra dispersion in magnitude {\green $\hat{m}_B$} (from coherent scatter) is absorbed completely by the width of the underlying magnitude population (discussed in Section \ref{sec:underlying}) without introducing cosmological bias, which is not true of the colour term, hence the requirement for modelling additional colour dispersion. Tests on incorporating extra dispersion on stretch as well show that stretch is less biased than colour, and cause negligible bias in cosmology.

As shown in \citep{Kessler2013}, the extra colour dispersion shows heavy redshift dependence, increasing with redshift. As the extra dispersion may arise from underlying supernova physics, rather than {\green any selection or observational effects}, we decide to incorporate redshift dependence in our extra uncertainty. We thus add $\kappa_0 + \kappa_1 z$ to our observed colour uncertainty (in quadrature). The $\kappa$ parameters are highly degenerate with the width of the intrinsic colour population $\sigma_c$. We subject them to Cauchy priors centered on zero and with width $0.05$, where $\kappa$ is bounded between $0$ and $0.05$. We pick this maximum value to allow extra dispersion without completely subsuming the intrinsic population widths due to the severe degeneracy, where this maximum value easily encapsulates the determined dispersion according to the results of \citet{Kessler2013}. As such, our combined covariance on the observation $\hat{\eta}$ is given by $\mathcal{C}_{\rm tot} = \mathcal{C} + {\rm DiagMatrix}\left[0, 0, (\kappa_0 + \kappa_1 z)^2\right]$.

@@

In order to verify our model we run it through stringent tests. First, we validate on toy models, verifying that we recover accurate cosmology {\green when generating fake supernovae data constructed to satisfy the assumptions of the BHM construction}. We then validate our model on SNANA simulations based on a collection of low redshift surveys and the DES three-year spectroscopic sample.

@@

\begin{enumerate}[1.]
	\item Draw a redshift from a power law distribution. For the low redshift survey this is $\mathcal{U}(0.0004, 0.01)^{0.5}$, and for the DES-like survey this is $\mathcal{U}(0.008, 1.0)^{0.3}$.
	\item Draw a random mass probability from $\mathcal{U}(0, 1)$ and calculate the mass-brightness correction using $\delta(0) = 0.08$, $\delta(0)/\delta(\infty) = 0.5$, and equation \eqref{eq:mass}.
	\item Draw an absolute magnitude, stretch and colour from the respective distributions $\mathcal{N}(-19.3, 0.1)$, $\mathcal{N}(0, 1)$, $\mathcal{N}(0, 0.1)$. {\green Calculate the true absolute magnitude using Equation \eqref{eq:l2}.}
	\item Calculate $\mu(z)$ given the drawn redshift and cosmological parameters $\Omega_m = 0.3$, $w = -1$ under Flat $\Lambda$CDM cosmology. Use this to determine the true apparent magnitude of the object $m_B$.
	\item Determine if the SNIa is detected using detection probability $P(S|m_B) = \mathcal{N}^{\rm skew}(13.72, 1.35, 5.87)$ for the low redshift survey (numeric values obtained by fitting to existing low redshift data). For the DES-like survey, accept with probability $P(S|m_B) = \Phi^C(23.14, 0.5)$. Repeat from step one until we have a supernova that passes. {\green We use realistic values for the selection probability to ensure our model is numerically stable with highly skewed selection functions.}
	\item Add independent, Gaussian observational error onto the true $m_B$, $x_1$, $c$ using Gaussian widths of $0.04$, $0.2$, $0.03$ respectively (following the mean uncertainty for DES-like SNANA simulations). Add extra colour uncertainty in quadrature of $\kappa_0 + \kappa_1 z$, where $\kappa_0 = \kappa_1 = 0.03$.
\end{enumerate}

The selection functions (a skew normal for low-redshift and an error function for high-redshift) are given independent uncertainty of $0.01$ on all parameters (mean and width for the CDF selection function, and mean, width and skewness for the skew normal selection function). Draw from each survey simulation until we have 1000 LowZ supernovae and 1000 DES-like supernovae, representing a statistical sample of greater power than the estimated 350 supernovae for the combined DES three-year and low-redshift spectroscopic analysis. Sample data for 1000 high and low redshift supernovae are shown in Figure \ref{fig:simple_pop}, confirming the presence of strong selection effects in both toy surveys, as designed.

@@

{\red motivate this better}

@@

Simulations (using the SNANA package) follow the observational schedule and observing conditions for the DES and LowZ surveys, where the LowZ sample is comprised of CfA3 \citep{Hicken2009, Hicken2009a}, CfA4 \citep{Hicken2012} and CSP \citep{Contreras2010,Folatelli2010,Stritzinger2011}. Simulation specifics can be found in \citet{Kessler18}.

In addition to the improvements in the scatter models over the simple data, we also include peculiar velocities for the LowZ sample, and our full treatment of systematics. Our simulated populations are sourced from \citet[][hereafter {\sk}]{Scolnic2016} and shown in Table \ref{tab:dist}. Initial tests were also done with a second, Gaussian population with colour and stretch populations centered on zero and with respective width $0.1$ and $1$, however cosmological parameters were not impacted by choice of the underlying population and we continue using only the {\sk} population for computational efficiency. The selection effects were quantified by comparing all the generated supernovae to those that pass our cuts, as shown in Figure~\ref{fig:sf_snana}. It is from this simulation that our analytic determination of the selection functions for the LowZ and DES survey are based. We run two simulations to determine the efficiency using the {\gten} and {\celeven} scatter models and find no difference in the Malmquist bias between the two models.

@@

\begin{table*}
	\centering
	\caption{Standardisation parameters and base intrinsic scatter parameter results for the 100 fits to {\gten} and {\celeven} simulations. We show the average parameter mean and {\green average }standard deviation, with the simulation scatter shown in brackets. Truth values for the simulations are $\alpha=0.15$, $\langle M_B \rangle = -19.365$, $\beta_{\rm G10} = 3.1$, $\beta_{\rm C11} = 3.8$.  The width of the intrinsic scatter does not have an input truth value as it is determined from the scatter model, with {\gten} having 70\% achromatic scatter and {\celeven} only having 25\% achromatic scatter.}
	\label{tab:standardisation}
	\begin{tabular}{l|ccccc}
		\hline
		Model & $\alpha$ & $\beta$ & $\langle M_B \rangle$ & $\sigma_{m_B}^0$ &  $\sigma_{m_B}^1$ \\
		\hline
		{\gten} Stat + Syst  & $0.152\pm0.009\ (0.008)$ & $ 3.44\pm0.19\ (0.18)$ & $-19.367\pm0.028\ (0.015)$ & $0.070\pm0.022\ (0.018)$ & $0.073\pm0.025\ (0.022)$\\
		{\gten}  Stat         & $0.150\pm0.008\ (0.008)$ & $3.43\pm0.20\ (0.17)$ & $-19.374\pm0.016\ (0.013)$ & $0.069\pm0.023\ (0.019)$ & $0.072\pm0.026\ (0.023)$\\
		{\celeven} Stat + Syst  &  $0.152\pm0.009\ (0.007)$ & $3.76\pm0.15\ (0.13)$ & $-19.351\pm0.030\ (0.018)$ & $0.024\pm0.016\ (0.011)$ & $0.029\pm0.020\ (0.014)$ \\
		{\celeven} Stat         &  $0.150\pm0.008\ (0.007)$ & $3.75\pm0.16\ (0.13)$ & $-19.359\pm0.016\ (0.015)$ & $0.025\pm0.016\ (0.012)$ & $0.027\pm0.020\ (0.015)$\\
		\hline
	\end{tabular}
\end{table*}

@@

\begin{table}
	\centering
	\caption{Reduced parameter correlations with $w$ for the combined 100 simulation fits. Correlations for the LowZ band systematics and the latent parameters representing selection function uncertainty are not shown but have negligible correlation.}
	\label{tab:parameter_correlations}
	\begin{tabular}{c|cc}
		Parameter & {\gten} Stat+Syst & {\celeven} Stat+Syst  \\
		\hline
		$\Omega_m$ &   -0.19 &     -0.21     \\
		$\alpha$ &   -0.17 &     -0.20     \\
		$\beta$ &   -0.29 &     -0.23     \\
		$\langle M_B \rangle$ &    0.68 &      0.66     \\
		$\sigma_{\rm m_B}^{0}$ &    0.04 &      0.07     \\
		$\sigma_{\rm m_B}^{1}$ &    0.23 &      0.18     \\
		$\sigma_{x_1}^{0}$ &    0.04 &      0.03     \\
		$\sigma_{x_1}^{1}$ &    0.05 &      0.01     \\
		$\sigma_{c}^{0}$ &    0.01 &      0.11     \\
		$\sigma_{c}^{1}$ &    0.08 &      0.04     \\
		$\alpha_c^{0}$ &   -0.04 &      0.04     \\
		$\alpha_c^{1}$ &    0.03 &      0.01     \\
		$\kappa_{c0}^{0}$ &   -0.10 &     -0.05     \\
		$\kappa_{c0}^{1}$ &   -0.20 &     -0.17     \\
		$\kappa_{c1}^{0}$ &   -0.05 &     -0.01     \\
		$\kappa_{c1}^{1}$ &   -0.01 &      0.01     \\
		%$s_c^{0}$ &    0.00 &      0.01     \\
		$\delta(0)$ &    0.00 &      0.00     \\
		$\delta(\infty)/\delta(0)$ &    0.00 &      0.00     \\
		$\langle x_1^{0} \rangle$ &   -0.01 &     -0.05     \\
		$\langle x_1^{1} \rangle$ &   -0.02 &      0.02     \\
		$\langle x_1^{2} \rangle$ &   -0.04 &     -0.04     \\
		$\langle x_1^{3} \rangle$ &   -0.03 &     -0.06     \\
		$\langle x_1^{4} \rangle$ &   -0.06 &     -0.06     \\
		$\langle x_1^{5} \rangle$ &    0.04 &      0.02     \\
		$\langle x_1^{6} \rangle$ &    0.04 &      0.04     \\
		$\langle x_1^{7} \rangle$ &    0.08 &      0.03     \\
		$\langle c^{0} \rangle$ &   -0.05 &     -0.12     \\
		$\langle c^{1} \rangle$ &    0.11 &      0.03     \\
		$\langle c^{2} \rangle$ &    0.11 &      0.06     \\
		$\langle c^{3} \rangle$ &    0.14 &      0.04     \\
		$\langle c^{4} \rangle$ &   -0.11 &     -0.11     \\
		$\langle c^{5} \rangle$ &   -0.15 &     -0.08     \\
		$\langle c^{6} \rangle$ &   -0.12 &     -0.13     \\
		$\langle c^{7} \rangle$ &   -0.12 &     -0.06     \\
		$\delta [ {\rm SALT}_0 ]$ &    0.05 &      0.05     \\
		$\delta [ {\rm SALT}_1 ]$ &   -0.01 &      0.02     \\
		$\delta [ {\rm SALT}_2 ]$ &   -0.10 &     -0.09     \\
		$\delta [ {\rm SALT}_3 ]$ &   -0.03 &     -0.03     \\
		$\delta [ {\rm SALT}_4 ]$ &    0.08 &      0.09     \\
		$\delta [ {\rm SALT}_5 ]$ &    0.01 &      0.02     \\
		$\delta [ {\rm SALT}_6 ]$ &    0.05 &      0.07     \\
		$\delta [ {\rm SALT}_7 ]$ &   -0.11 &     -0.10     \\
		$\delta [ {\rm SALT}_8 ]$ &    0.01 &      0.02     \\
		$\delta [ {\rm SALT}_9 ]$ &    0.02 &      0.02     \\
		$\delta [ {\rm MWE}_{B-V} ]$ &    0.03 &      0.02     \\
		$\delta [ {\rm HST Calib} ]$ &   -0.07 &     -0.07     \\
		$\delta [ v_{\rm pec} ]$ &    0.00 &     -0.01     \\
		$\delta [ {\rm \delta z } ]$ &    0.01 &      0.00     \\
		$\delta [ \Delta g ]$ &    0.05 &      0.11     \\
		$\delta [ \Delta r ]$ &    0.16 &      0.10     \\
		$\delta [ \Delta i ]$ &   -0.16 &     -0.18     \\
		$\delta [ \Delta z ]$ &   -0.26 &     -0.26     \\
		$\delta [ \Delta \lambda_g ]$ &    0.16 &      0.20     \\
		$\delta [ \Delta \lambda_r ]$ &    0.05 &      0.06     \\
		$\delta [ \Delta \lambda_i ]$ &    0.00 &     -0.01     \\
		$\delta [ \Delta \lambda_z ]$ &    0.09 &      0.07     \\
		\hline
	\end{tabular}
\end{table}

@@

Points of maximum posterior for 100 data realisations are shown in Figure \ref{fig:bulk_posterior}. The parameter bounds and biases for $w$ are listed in Table \ref{tab:bulk_summary},  and secondary parameters are shown in Table \ref{tab:standardisation}. Our recovered results for $w$ are all within $0.5\sigma$ of the true values of $w=-1$. Table \ref{tab:standardisation} shows a clear difference in both $\beta$ and $\sigma_{m_B}$ across the {\gten} and {\celeven} simulations. As expected, the {\celeven} simulations recover a far smaller intrinsic magnitude scatter, giving results of approximately $0.025$ when compared to the result of $0.070$ for the {\gten} simulations. The extra smearing of the {\celeven} {\green model does not result in a significantly biased $\beta$ value compared to the average uncertainty on $\beta$}, with recovery of $\beta\approx3.76$ close to the input truth value of $3.8$, however the $\beta$ recovery for the {\gten} simulations is biased high, finding $\beta\approx3.44$ with an input of $3.1$. Interestingly, $w$-bias is only found for the {\celeven} simulations.

@@

We compare the results of our model against those of the BBC method \citep{Kessler2017}. BBC has been used in prior analyses, such as the Pantheon sample analysis of \citet{Scolnic2017}. {\green The BBC method is a two-part process, BBC computes bias corrections for observables, and then the corrected observables are fit using CosmoMC \citep{lewis2002cosmomc}. For shorthand, we refer to this combined process as the BBC method in this paper, as we are concerned with the results of cosmological parameter inference.} As a leading supernova cosmology method, it provides a good consistency as to the current levels of accuracy in recovering cosmological parameters.

To this end, we take the results of the BBC method also run on {\green the} set of 200 validation simulations and compare the recovered $w$ values to those of our method. The results are detailed in Table \ref{tab:bulk_summary_bbc}, and a scatter plot of the simulation results is presented in Figure \ref{fig:bulk_comparison}.

@@

\begin{table}
	\centering
	\caption{Characterising the bias on $w$ using the 100 simulations for the {\gten} scatter model and 100 simulations for {\celeven} scatter model. We also show the results when combining the {\gten} and {\celeven} models into a combined set of 200 simulations. The mean $w$ value for our method and BBC are presented, along with the mean when averaging the difference between our method and BBC for each individual simulation. Finally, we also characterise the scatter between the methods in the final row. Averages are computed giving each simulation sample the same weight. In the model, $\Delta$ represents Steve - BBC. The final row shows the scatter between Steve and BBC for the different simulations.}
	\label{tab:bulk_summary_bbc}
	\begin{tabular}{l|ccc}
		\hline
		Model & {\gten} & {\celeven} & ({\gten} + {\celeven}) \\
		\hline
		Steve $\langle w \rangle$           & $-0.998\pm0.007$ & $-0.945\pm0.007$ & $-0.972\pm0.006$\\
		BBC $\langle w \rangle$             & $-1.044\pm0.006$ & $-0.978\pm0.007$ & $-1.010\pm0.005$ \\
		$\Delta$  $\langle w \rangle$  & $+0.044\pm0.006$ & $+0.033\pm0.006$ & $+0.038\pm0.004$ \\
		\hline
		$\Delta$  $\sigma_w$           & $0.057\pm0.004$ & $0.062\pm0.004$ & $0.060\pm0.003$ \\
		\hline
	\end{tabular}
\end{table}
